Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding $z\sim2$ Quasars

### 2017-09-28 QPQ9/Submit/qpq9_resubmit.tex
resubmission, after bolding

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$. 
We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in 
absorption. The sample selects foreground quasars with precise redshift measurements, using 
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the 
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the 
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4}, 
and \ion{Mg}{2}. We find that the mean absorptions exhibit large velocity widths 
$\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational 
motion and Hubble flow, and galactic-scale outflows are not required to explain the large 
widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift. 
The mean absorption centroids exhibit small redshift relative to the 
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid 
velocities of the individual absorption systems. We show that the observed offsets may be produced 
if (i) the ionizing radiation from the foreground quasars is anisotropic or intermittent; (ii) the 
gas is not flowing into the galaxy.  
\end{abstract}

@@

With absorption-line spectroscopy of background sightlines, other researchers also have had 
success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net 
large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on 
1\textendash2\,Mpc scales. \cite{Ho+17} found gas spiraling inward near the disk plane of 
star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding 
$z\sim1$ quasars. They found large peculiar motions in the gas exceeding the expected virial 
velocity, with quasar-driven outflows being one possible explanation. However, we consider that 
their velocity spreads can be better quantified. Other 
existing studies that found large velocity spreads are limited to single sightlines with most of 
the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11,RudieNewmanMurphy17}, 
or with gas tracing 
a higher ionization state than the QPQ absorption systems \citep[e.g., ][]{Churchill+12}, or where 
the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier13}, where a
single sightline is reported, the $\Delta v_{90}$ of the \ion{Mg}{2} absorption is less than the 
average of the QPQ8 \ion{C}{2} absorption. In \cite{Muzahid+15}, an absorber is found with 
$\Delta v_{90}$ smaller than $555\,{\rm km\,s^{-1}}$ in \ion{O}{6} and \ion{N}{5}, and still 
smaller for other ions. The \cite{Zahedy+16} sample likewise has average $\Delta v_{90}$ smaller 
than that of QPQ8.

@@

In this paper (hereafter QPQ9), we examine the flows of gas in the environments of massive 
galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
\citep[][hereafter QPQ1]{QPQ1} to use the standard techniques of absorption-line spectroscopy 
with background quasars. These quasar pairs 
have angular separations that correspond to less than 300\,kpc projected separation at the 
foreground quasar's redshift. Our previous publications from these quasar pairs have established 
that these galaxies are surrounded by a massive, cool, and enriched CGM 
\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 102 background 
spectra that are paired with foreground quasars with precisely measured redshifts. Among the
sightlines in the QPQ9 sample, 13 have spectral resolution $R>5000$ from echellette or echelle
observations, and have been analyzed separately in QPQ8 (see their Figure 8, 9, and 10, and their 
Appendix). In QPQ8, where the individual metal-bearing absorption components are resolved, 15 out 
of the 21 components are at positive velocities relative to the systemic redshift. For this
current work, we stack spectra of all resolutions instead of performing a component-by-component
analysis. Our primary scientific interests are twofold: (i) search for signatures of galactic-scale
outflows from the central galaxy, presumably driven by recent star formation and/or active galactic
nuclei feedback; (ii) characterize the dynamics of the gas around these massive systems. We further
describe an aspect of this experiment that offers a unique opportunity to study galactic-scale
flows: we argue that, the anisotropic or intermittent radiation from the foreground quasars may
break the symmetry in the velocity field of circumgalactic absorbers. If the ionizing radiation
field is asymmetric, the absorbers may also distribute asymmetrically. Alternatively, finite quasar
lifetime will result in different radiation fields impinged on the gas closer to versus further
away from the background quasar, due to different light travel times. \cite{KirkmanTytler08}
reported an asymmetry in \ion{H}{1} absorption on scales larger than the CGM, and gave similar
arguments on anisotropy or intermittence.

@@

We adopt a $\Lambda$CDM cosmology with $\Omega_M=0.26, \Omega_\Lambda=0.74$, and 
$H_0=70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. Distances are proper unless otherwise stated. When referring 
to comoving distances we include explicitly an $h^{-1}$ term and follow modern convention of 
scaling to the Hubble constant $h = H_0/(70\,{\rm km\,s^{-1}\,Mpc^{-1}})$.
%All equivalent width measurements are presented in the rest-frame, unless otherwise specified.

@@

From our QPQ survey\footnote{http://www.qpqsurvey.org}, we analyze a subset of systems that 
pass within transverse separation $R_\perp<300$\,kpc from a foreground quasar with 
$z_{\rm fg} > 1.6$. We restrict the sample to foreground quasars with redshift measured from 
\ion{Mg}{2}\,2800, [\ion{O}{3}]\,5007, or H$\alpha$ emission, giving a precision of 
$300\,{\rm km\,s^{-1}}$ or better and an average offset from the systemic redshift of 
$|100\,{\rm km\,s^{-1}}|$ or less. According to \cite{Shen+16}, the [\ion{O}{3}] emission-line 
redshifts have the smallest scatter (intrinsic scatter and measurement error combined) of 
$68\,{\rm km\,s^{-1}}$ about the systemic redshift, and we analyze the sub-sample with 
[\ion{O}{3}] redshifts separately. The [\ion{O}{3}] line has an average blueshift of 
$48\,{\rm km\,s^{-1}}$ about the systemic redshift, which has been added when we compute the 
redshift of the line. The scatter and average offset of [\ion{O}{3}] redshifts reported by 
\cite{Shen+16} is consistent with the numbers reported by \cite{Boroson05} using a larger but 
lower redshift sample. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
$226\,{\rm km\,s^{-1}}$ according to \cite{Shen+16}, and we have taken into account their 
reported median blueshift of $57\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from the systemic. We note that 
\cite{Richards+02} reported a median redshift of $97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from 
[\ion{O}{3}] using a larger but lower redshift sample. In QPQ8, we quantified 
the precision of H$\alpha$ to be $300\,{\rm km\,s^{-1}}$ and the median offset from the systemic 
redshift is close to zero, consistent with the velocity shifts measured by \cite{Shen+11}. 
Although H$\beta$ is a narrow emission-line, we do not consider its redshift sufficiently reliable 
for use as systemic redshift. H$\beta$ redshifts have a large scatter about the systemic 
$\approx400\,{\rm km\,s^{-1}}$, and a large average offset about the systemic 
$\approx100\,{\rm km\,s^{-1}}$ \citep[][QPQ8]{Shen+16}.
Our line-centering algorithm calculates the mode of a line given by
$3\times{\rm median}-2\times{\rm mean}$, applied to the upper 60\% of the emission, while
\cite{Shen+16} calculates the peak of a line. We expect that our line-centering algorithm gives
emission redshifts very comparable to the \cite{Shen+16} algorithm, however. \cite{Shen+16}
states that the difference between the peak and the centroid of an emission-line
is not significant except for the broad line H$\beta$, which we do not use in redshift
measurements. To quantify the above, we further obtain individual measurements of centroids and
peaks in the \cite{Shen+16} sample through private communication. We found there is essentially no
difference between using the centroid versus using the peak for [\ion{O}{3}] emission redshifts,
and there is on average $50\,{\rm km\,s^{-1}}$ difference for \ion{Mg}{2}. We may expect the
difference between the mode and the peak is even smaller. Hence, we argue that the average
systemic bias corrections measured in \cite{Shen+16} may be self-consistently applied to our
measured emission-line redshifts to obtain systemic redshifts.

We further add to the QPQ dataset with quasar pairs selected from the public dataset of 
igmspec\footnote{https://github.com/specdb/igmspec} \citep{Prochaska+17}, which includes the 
spectra from the quasar catalogs based upon the Sloan Digital Sky Survey Seventh Data Release 
\citep{Schneider+10} and the Twelfth Data Release \citep{Paris+17}. We only select pairs with 
$z_{\rm fg}$ measurable using a robust \ion{Mg}{2}\,2800 emission-line. 
We reach a final sample size of 102. 
Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
QPQ publications for the details on the emission-line centering algorithm, data reduction, and
continuum normalization (QPQ1; QPQ6; QPQ8).

@@

\begin{figure}
%\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
\includegraphics[width=3.5in]{f02.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thin, 
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away 
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thick, blue. 
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
included in the modeling. The absorptions frequently exhibit large velocity widths. The dashed 
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The 
$1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack are 
$25\,{\rm km\,s^{-1}}$ and $27\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling
errors of the other stacks.
}
\label{fig:stacks_and_fits}
\end{figure}

We create composite spectra that average over the intrinsic scatter in quasar environments, 
continuum placement errors, and redshift errors. The individual spectra of background quasars are 
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum 
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to 
a common spectral resolution. The individual spectra are then combined with a mean or a median 
statistic. Bad pixels in the individual spectra have been masked before generating the 
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the 
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather 
than scatter in the flux of individual observations. The mean statistic of the individual spectra 
yields a good estimate of the average absorption and preserves equivalent width. The median 
statistic is less sensitive to outliers, however the median opacity at any velocity channel is 
rather small, since the discrete absorbers are spread throughout the entire velocity window. The 
analysis on the median velocity field is thus subject to larger uncertainty. In the following we 
present stacked spectra using both the mean and the median statistic.

In Figure~\ref{fig:stacks_and_fits}, we present mean and median stacks of \ion{C}{2}\,1334, 
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 absorption of the QPQ9 sample. We focus on the 
analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
and it is more challenging to analyze their kinematics.
%To assess the average absorption of these transitions,
%we have combined the data with a novel technique.
%We have fitted the combined dataset using a cubic b-spline
%with knots at every 100\,kms.  We weighted each data
%point by the velocity width of the pixel to insure that 
%each sightline makes an equal contribution to the stack.
%These b-spline profiles are presented in the figure
%and a trivial integration gives the reported equivalent
%widths.
%[consider down-weighting systems with $<3\sigma$ EW]
%[Comnent on EW from 'standard' technique]
Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
skewed toward positive velocities. We have 40 pairs in the QPQ9 sample for \ion{C}{2} analysis
and an even larger number of pairs for \ion{C}{4} and \ion{Mg}{2} analyses, and the total number
of individual components can only be larger than the number of absorption systems. Hence, although
QPQ8 showed the distribution of absorbing components in velocity is non-Gaussian for each
individual quasar-host associated system, the central limit theorem applies and the distribution
of all absorbing components should tend toward Gaussian distribution. A visual inspection of the 
stack confirms that a broader absorption component is not apparent. Therefore, to model the 
absorption, we may introduce a Gaussian profile while allowing a constant pseudo-continuum level 
to vary. We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit 
to the data, we measure the centroid of the \ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$ and
the $1\sigma$ dispersion to be $293\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that
contradicts the standard expectation, while the dispersion suggests extreme kinematics. The median 
stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid with 
smaller offset and comparable dispersion.

We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the 
absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at 
$+235\,{\rm km\,s^{-1}}$, and a dispersion of $330\,{\rm km\,s^{-1}}$, consistent with the full
sample.

To model the mean and median absorption of \ion{C}{4}\,1548 and \ion{Mg}{2}\,1796, we introduce a  
second Gaussian with separation equal to the doublet separation ($498\,{\rm km\,s^{-1}}$ and 
$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. We
allow the doublet ratio to vary from 2:1 to 1:1. The modeling results show that the velocity fields
of \ion{C}{4} and \ion{Mg}{2} are consistent with \ion{C}{2}, i.e.\ large dispersion and centroid
is skewed toward positive velocities.

@@

Given the small sample size, one must scrutinize the statistical significance of the measured 
velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile 
to model each bootstrap realization, and quote the standard deviation in the bootstrap 
realizations to be the scatter in the centroids of the data. The scatters 
$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic 
variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show 
the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We 
find that 97\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper
limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
$\delta v<+526\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} 
absorption.

One may also ask whether the measured positive offsets come from systematic bias in redshift 
measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, the 
[\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically 
less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean 
stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a redshift measured from the
more symmetric \ion{Mg}{2} or H$\alpha$ emission when available. We are able to replace for 11 out
of the 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
velocity structure and again shows a positive offset $\approx+303\,{\rm km\,s^{-1}}$. We thus
conclude that our algorithm for measuring redshifts is not severely biased by the blue wing of the
[\ion{O}{3}] emission-line.

>>>>

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$. 
We employ {\bf 148} projected quasar pairs to study the circumgalactic gas of the foreground quasars in
absorption. The sample selects foreground quasars with precise redshift measurements, using 
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the 
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the 
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4}, 
and \ion{Mg}{2}. We find that the mean absorptions exhibit large velocity widths 
$\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational 
motion and Hubble flow, and galactic-scale outflows {\bf are not required} to explain the large
widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift. 
The mean absorption centroids exhibit small redshift relative to the 
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid 
velocities of the individual absorption systems. We show that the observed offsets may be produced 
if (i) the ionizing radiation from the foreground quasars is anisotropic or intermittent; (ii) the 
gas is not flowing into the galaxy.  
\end{abstract}

@@

With absorption-line spectroscopy of background sightlines, other researchers also have had 
success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net 
large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on 
1\textendash2\,Mpc scales. \cite{Ho+17} found gas spiraling inward near the disk plane of 
star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding 
$z\sim1$ {\bf quasars. They found large peculiar motions in the gas exceeding the expected virial
velocity, with quasar-driven outflows being one possible explanation. However, we consider that 
their velocity spreads can be better quantified.} Other
existing studies that found large velocity spreads are limited to single sightlines with most of 
the gas within several hundred ${\rm km\,s^{-1}}$ {\bf \citep[e.g., ][]{Tripp+11,RudieNewmanMurphy17}},
or with gas tracing 
a higher ionization state than the QPQ absorption systems \citep[e.g., ][]{Churchill+12}, or where 
the average velocity spread is smaller than that measured in {\bf QPQ8. In \cite{Gauthier13}, where a
single sightline is reported, the $\Delta v_{90}$ of the \ion{Mg}{2} absorption is less than the 
average of the QPQ8 \ion{C}{2} absorption. In \cite{Muzahid+15}, an absorber is found with 
$\Delta v_{90}$ smaller than $555\,{\rm km\,s^{-1}}$ in \ion{O}{6} and \ion{N}{5}, and still 
smaller for other ions. The \cite{Zahedy+16} sample likewise has average $\Delta v_{90}$ smaller 
than that of QPQ8.}

@@

In this paper (hereafter QPQ9), we examine the flows of gas in the environments of massive 
galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
\citep[][hereafter QPQ1]{QPQ1} to use the standard techniques of absorption-line spectroscopy 
with background quasars. These quasar pairs 
have angular separations that correspond to less than 300\,kpc projected separation at the 
foreground quasar's redshift. Our previous publications from these quasar pairs have established 
that these galaxies are surrounded by a massive, cool, and enriched CGM 
\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of {\bf 148} background
spectra that are paired with foreground quasars with precisely measured redshifts. Among the
sightlines in the QPQ9 sample, 13 have spectral resolution $R>5000$ from echellette or echelle
observations, and have been analyzed separately in QPQ8 {\bf (see their Figure 8, 9, and 10, and their
Appendix). In QPQ8, where the individual metal-bearing absorption components are resolved, 15 out
of the 21 components are at positive velocities relative to the systemic redshift. For this
current work, we stack spectra of all resolutions instead of performing a component-by-component
analysis.} Our primary scientific interests are twofold: (i) search for signatures of galactic-scale
outflows from the central galaxy, presumably driven by recent star formation and/or active galactic
nuclei feedback; (ii) characterize the dynamics of the gas around these massive systems. We further
describe an aspect of this experiment that offers a unique opportunity to study galactic-scale
flows: we argue that, the anisotropic or intermittent radiation from the foreground quasars may
break the symmetry in the velocity field of circumgalactic absorbers. If the ionizing radiation
field is asymmetric, the absorbers may also distribute asymmetrically. Alternatively, finite quasar
lifetime will result in different radiation fields impinged on the gas closer to versus further
away from the background quasar, due to different light travel times. \cite{KirkmanTytler08}
reported an asymmetry in \ion{H}{1} absorption on scales larger than the CGM, and gave similar
arguments on anisotropy or intermittence.

@@

We adopt a $\Lambda$CDM cosmology with $\Omega_M=0.26, \Omega_\Lambda=0.74$, and 
$H_0=70\,{\rm km\,s^{-1}\,Mpc^{-1}}$. Distances are proper unless otherwise stated. When referring 
to comoving distances we include explicitly an $h^{-1}$ term and follow modern convention of 
scaling to {\bf the Hubble constant $h = H_0/(70\,{\rm km\,s^{-1}\,Mpc^{-1}})$}.
%All equivalent width measurements are presented in the rest-frame, unless otherwise specified.

@@

From our QPQ survey\footnote{http://www.qpqsurvey.org}, we analyze a subset of systems that 
pass within transverse separation $R_\perp<300$\,kpc from a foreground quasar with 
$z_{\rm fg} > 1.6$. We restrict the sample to foreground quasars with redshift measured from 
\ion{Mg}{2}\,2800, [\ion{O}{3}]\,5007, or H$\alpha$ emission, giving a precision of 
$300\,{\rm km\,s^{-1}}$ or better and an average offset from the systemic redshift of 
$|100\,{\rm km\,s^{-1}}|$ or less. According to \cite{Shen+16}, the [\ion{O}{3}] emission-line 
redshifts have the smallest scatter (intrinsic scatter and measurement error combined) of 
$68\,{\rm km\,s^{-1}}$ about the systemic redshift, and we analyze the sub-sample with 
[\ion{O}{3}] redshifts separately. The [\ion{O}{3}] line has an average blueshift of 
$48\,{\rm km\,s^{-1}}$ about the systemic redshift, which has been added when we compute the 
redshift of the line. The scatter and average offset of [\ion{O}{3}] redshifts reported by 
\cite{Shen+16} is consistent with the numbers reported by \cite{Boroson05} using a larger but 
lower redshift sample. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
$226\,{\rm km\,s^{-1}}$ according to \cite{Shen+16}, and we have taken into account their 
reported median blueshift of $57\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from the systemic. We note that 
\cite{Richards+02} reported a median redshift of $97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from 
[\ion{O}{3}] using a larger but lower redshift sample. In QPQ8, we quantified 
the precision of H$\alpha$ to be $300\,{\rm km\,s^{-1}}$ and the median offset from the systemic 
redshift is close to zero, consistent with the velocity shifts measured by \cite{Shen+11}. 
Although H$\beta$ is a narrow emission-line, we do not consider its redshift sufficiently reliable 
for use as systemic redshift. H$\beta$ redshifts have a large scatter about the systemic 
$\approx400\,{\rm km\,s^{-1}}$, and a large average offset about the systemic 
$\approx100\,{\rm km\,s^{-1}}$ \citep[][QPQ8]{Shen+16}.
{\bf Our line-centering algorithm calculates the mode of a line given by
$3\times{\rm median}-2\times{\rm mean}$, applied to the upper 60\% of the emission, while
\cite{Shen+16} calculates the peak of a line. We expect that our line-centering algorithm gives
emission redshifts very comparable to the \cite{Shen+16} algorithm, however. \cite{Shen+16}
states that the difference between the peak and the centroid of an emission-line
is not significant except for the broad line H$\beta$, which we do not use in redshift
measurements. To quantify the above, we further obtain individual measurements of centroids and
peaks in the \cite{Shen+16} sample through private communication. We found there is essentially no
difference between using the centroid versus using the peak for [\ion{O}{3}] emission redshifts,
and there is on average $50\,{\rm km\,s^{-1}}$ difference for \ion{Mg}{2}. We may expect the
difference between the mode and the peak is even smaller. Hence, we argue that the average
systemic bias corrections measured in \cite{Shen+16} may be self-consistently applied to our
measured emission-line redshifts to obtain systemic redshifts.}

We further add to the QPQ dataset with quasar pairs selected from the public dataset of 
igmspec\footnote{https://github.com/specdb/igmspec} \citep{Prochaska+17}, which includes the 
spectra from the quasar catalogs based upon the Sloan Digital Sky Survey Seventh Data Release 
\citep{Schneider+10} and the Twelfth Data Release \citep{Paris+17}. {\bf We only select pairs with
$z_{\rm fg}$ measurable using a robust \ion{Mg}{2}\,2800 emission-line. 
We reach a final sample size of 148.}
Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
QPQ publications for the details on the {\bf emission-line centering} algorithm, data reduction, and
continuum normalization (QPQ1; QPQ6; QPQ8).

@@

\begin{figure}
%\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
\includegraphics[width=3.5in]{f02.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thin, 
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away 
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thick, blue. 
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
included in the modeling. The absorptions frequently exhibit large velocity widths. The {\bf blue} dashed
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The 
$1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack {\bf are
$25\,{\rm km\,s^{-1}}$ and $27\,{\rm km\,s^{-1}}$} respectively, which is also the typical modeling
errors of the other stacks.
}
\label{fig:stacks_and_fits}
\end{figure}

We create composite spectra that average over the intrinsic scatter in quasar environments, 
continuum placement errors, and redshift errors. The individual spectra of background quasars are 
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum 
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to 
a common spectral resolution. The individual spectra are then combined with a mean or a median 
statistic. Bad pixels in the individual spectra have been masked before generating the 
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the 
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather 
than scatter in the flux of individual observations. The mean statistic of the individual spectra 
yields a good estimate of the average absorption and preserves equivalent width. The median 
statistic is less sensitive to outliers, {\bf however the median opacity at any velocity channel is
rather small, since the discrete absorbers are spread throughout the entire velocity window. The 
analysis on the median velocity field is thus subject to larger uncertainty.} In the following we
present stacked spectra using both the mean and the median statistic.

In Figure~\ref{fig:stacks_and_fits}, we present mean and median stacks of \ion{C}{2}\,1334, 
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 absorption of the QPQ9 sample. We focus on the 
analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
and it is more challenging to {\bf analyze} their kinematics.
%To assess the average absorption of these transitions,
%we have combined the data with a novel technique.
%We have fitted the combined dataset using a cubic b-spline
%with knots at every 100\,kms.  We weighted each data
%point by the velocity width of the pixel to insure that 
%each sightline makes an equal contribution to the stack.
%These b-spline profiles are presented in the figure
%and a trivial integration gives the reported equivalent
%widths.
%[consider down-weighting systems with $<3\sigma$ EW]
%[Comnent on EW from 'standard' technique]
Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
skewed toward positive velocities. {\bf We have 40 pairs in the QPQ9 sample for \ion{C}{2} analysis
and an even larger number of pairs for \ion{C}{4} and \ion{Mg}{2} analyses, and the total number
of individual components can only be larger than the number of absorption systems. Hence, although
QPQ8 showed the distribution of absorbing components in velocity is non-Gaussian for each
individual quasar-host associated system, the central limit theorem applies and the distribution
of all absorbing components should tend toward Gaussian distribution. A visual inspection of the 
stack confirms that a broader absorption component is not apparent. Therefore, to} model the
absorption, we may introduce a Gaussian profile while allowing a constant pseudo-continuum level 
to vary. We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit 
to the data, we measure the centroid of the \ion{C}{2} stack {\bf to be \bf $+232\,{\rm km\,s^{-1}}$ and
the $1\sigma$ dispersion to be $293\,{\rm km\,s^{-1}}$.} The centroid suggests an asymmetry that
contradicts the standard expectation, while the dispersion suggests extreme kinematics. The median 
stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid with 
smaller offset and {\bf a more uncertain dispersion}.

We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the 
absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a {\bf centroid at
$+235\,{\rm km\,s^{-1}}$, and a dispersion of $330\,{\rm km\,s^{-1}}$,} consistent with the full
sample.

To model the mean and median absorption of \ion{C}{4}\,1548 and \ion{Mg}{2}\,1796, we introduce a  
second Gaussian with separation equal to the doublet separation ($498\,{\rm km\,s^{-1}}$ and 
$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. {\bf We
allow the doublet ratio to vary from 2:1 to 1:1.} The modeling results show that the velocity fields
of \ion{C}{4} and \ion{Mg}{2} are consistent with \ion{C}{2}, i.e.\ large dispersion and centroid
is skewed toward positive velocities.

@@

{\bf To assess the statistical significance of the measured velocity offsets, we perform a boostrap analysis by
randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile 
to model each bootstrap realization, and quote the standard deviation in the bootstrap 
realizations to be the scatter in the centroids of the data. The scatters 
$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic 
variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show 
the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We 
find that {\bf 97\%} of the centroids are at positive velocities. We place a generous $3\sigma$ upper
limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption {\bf at
$\delta v<+526\,{\rm km\,s^{-1}}$.} Given the large intrinsic scatter, we do not attempt to explore
whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} 
absorption.

One may also ask whether the measured positive offsets come from systematic bias in redshift 
measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, the 
[\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically 
less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean 
stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a redshift measured from the
more symmetric \ion{Mg}{2} or H$\alpha$ emission when available. We are able to replace for {\bf 11 out
of the} 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
velocity structure and again shows a positive {\bf offset $\approx+303\,{\rm km\,s^{-1}}$.} We thus
conclude that our algorithm for measuring redshifts is not severely biased by the blue wing of the
[\ion{O}{3}] emission-line.

Motivated by the study of \ion{Mg}{2} absorbers surrounding $z\sim1$ quasars by \cite{Johnson+15}, 
we also generate a mean-stacked spectrum for \ion{Mg}{2}\,2796 for lower redshift quasar pairs.  
We select quasars with $0.4<z_{\rm fg}<1.6$ and use the same other selection criteria as the main 
QPQ9 sample. The quasar pairs are selected from the igmspec database, with $z_{\rm fg}$ measured 
by \cite{HewettWild10}. For quasars with $z_{\rm fg}<0.84$, as redshift determination is dominated 
by [\ion{O}{3}] emission, a shift of $+48\,{\rm km\,s^{-1}}$ is applied to bring the emission-line 
redshift to the systemic. For quasars with $0.84<z_{\rm fg}<1.6$, as redshift determination is 
dominated by \ion{Mg}{2} emission, a shift of $+57\,{\rm km\,s^{-1}}$ is applied. There are {\bf 233}
pairs selected, with a median $z_{\rm fg}$ of 0.90 and a median $R_\perp$ of 208\,kpc. We present 
the mean stack in Figure~\ref{fig:stack_z1}. The absorption is weaker than the $z\sim2$ main QPQ9 
sample. Gaussian absorption models fitted to the stack recover a {\bf centroid of
$-11\pm379\,{\rm km\,s^{-1}}$ and a dispersion of $172\,{\rm km\,s^{-1}}$.} The average offset
from $0\,{\rm km\,s^{-1}}$ is much smaller than the offsets in the $z\sim2$ sample.
